---

title: "Trend Analysis for Crime in Los Angeles, California"
author: "Steven Nichols"
date: "December 14th, 2016"
output:
  html_document:
    highlight: tango
    keep_md: yes
    number_sections: yes
    theme: cerulean
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##load original file 
```{r, eval=FALSE, warning=FALSE}

setwd("C:\\Users\\Steven\\Google Drive\\1. MOT\\1) Fall 2016\\1. BA\\Assignments\\Midterm\\BA_Assignment\\Final\\LAPD_Crime_Analysis")

crime_groups <- read.csv("lapd_data.csv")

##set 2014 and 2015 dates to omit hour/minutes, as these do not appear in 2016 data 
crime_groups['Date_Standard'] <- format(as.POSIXct(strptime(crime_groups$Date_Rptd,"%m/%d/%Y",tz="")) ,format = "%m/%d/%Y")

##create date vector with just month and year 
crime_groups['Month_Year'] <- format(as.POSIXct(strptime(crime_groups$Date_Standard,"%m/%d/%Y",tz="")) ,format = "%m-%Y")

##set as Date DT
crime_groups$Date_Standard <- as.Date(crime_groups$Date_Standard, "%m/%d/%Y")

library(zoo)
##set as yearmon DT
crime_groups$Month_Year <- as.yearmon(crime_groups$Month_Year, "%m-%Y")

```

##remove unncesary vectors 

```{r, eval=FALSE, warning=FALSE}
crime_groups <- subset(crime_groups, select=c("Date_Standard", "Month_Year", "Area_Name", "Crm_Cd_Desc"))

```

##Bin categories into simpler subsets for analysis 
```{r,  eval=FALSE, warning=FALSE}


library(stringr)
library(dplyr)

crime_groups_cat <- crime_groups 

for (i in 1:nrow(crime_groups_cat)) {
  if (str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c("THEFT", 'SNATCHING', "SHOPLIFTING", "FRAUD", "PICKPOCKET", "embezzlement", "STOLEN", "STEALING"), collapse="|")) == TRUE) {
    crime_groups_cat$Category[i] <- "Theft"
  }
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c("ROBBERY", 'BURGLARY'), collapse="|")) == TRUE)
  {
    crime_groups_cat$Category[i] <- "Robbery"
  }
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c('MURDER', 'HOMICIDE'), collapse="|")) == TRUE)
  
  {
    crime_groups_cat$Category[i] <- "Homicide"
  }
  
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c('ARSON', 'VANDALISM'), collapse="|")) == TRUE)
  
  {
    crime_groups_cat$Category[i] <- "Arson/Vandalism"
  }
  
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c('SEX', 'ORAL', "ANNOYING", "MOLEST", "PEEPING", "RAPE", "INDECENT", "LEWD"), collapse="|")) == TRUE)
  
  {
    crime_groups_cat$Category[i] <- "Sexual"
  }
  
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c('ASSAULT', 'ASSUALTING', 'BATTERY'), collapse="|")) == TRUE)
  
  {
    crime_groups_cat$Category[i] <- "Assault"
  }
  
  else if(str_detect(crime_groups_cat$Crm_Cd_Desc[i], paste(c('CHILD', 'MINOR'), collapse="|")) == TRUE)
  
  {
    crime_groups_cat$Category[i] <- "Child_Abuse"
  }
  else  {
    crime_groups_cat$Category[i] <- "Other"
  }
}

##export output to CSV because of long run time

write.csv(crime_groups_cat, file="crime_groups_categorized.csv")



```

##read in document created in companion R code file 

```{r, warning=FALSE}

## read in CSV file and set category as factor 
crime_groups_cat <-read.csv("crimes_categorized.csv")

crime_groups_cat$Category <- as.factor(crime_groups_cat$Category)

```


## group dataset by area name and crime category, then tally crime incidences

```{r, warning=FALSE, include=FALSE}

library(dplyr)


```

```{r, warning=FALSE}



crime_groups <- crime_groups_cat %>% group_by(Month_Year, Area_Name, Category) %>% tally()


```

## calculate z-scores to determine outliers 

```{r, warning=FALSE}

##order dataset by crime_groups, area_name and category so that loop functions correctly 

crime_groups<- arrange(crime_groups, Area_Name, Category)

##instantiate vectors to hold values for loop 
crime_groups['running'] <- 0
crime_groups['mean'] <- 0
crime_groups['sd'] <- 0 
crime_groups['zscore'] <- 0 
crime_groups['row_num'] <- 0

##instantiate global counting variables 
n <- 1
start <- 1

##set first row equal to itself because of loop starting on second row 

crime_groups$running[1] <- crime_groups$n[1]
for (i in 2:nrow(crime_groups)) {
  if (crime_groups$Area_Name[i] == crime_groups$Area_Name[i-1] & crime_groups$Category[i] == crime_groups$Category[i-1]) {
    crime_groups$running[i] <- crime_groups$n[i] + crime_groups$running[i-1]
    n= n+1 
    
    
  }
  
  else {
    crime_groups$running[i] <- crime_groups$n[i]
    
    crime_groups$mean[i-1] <- crime_groups$running[i-1] / (n)
    mean <- crime_groups$mean[i-1]
    end <- i-1
    crime_groups$mean[start:end] <- mean
    sd <- sd(crime_groups$n[start:end])
    crime_groups$sd[start:end] <- sd
    crime_groups$row_num[start:end]<- n
    n=1
    start <- i
   
  }
  if (i == nrow(crime_groups)) {
    crime_groups$running[i] <- crime_groups$n[i] + crime_groups$running[i-1]
    crime_groups$mean[i] <- crime_groups$running[i] / (n)
    mean <- crime_groups$mean[i]
    end <- i
    crime_groups$mean[start:end] <- mean
    sd <- sd(crime_groups$n[start:end])
    crime_groups$sd[start:end] <- sd
    crime_groups$row_num[start:end]<- n

    
  }      
  
}

## calculate z-score outside of loop 
head(crime_groups)
crime_groups$zscore <- (crime_groups$n - crime_groups$mean) / crime_groups$sd
count <- 0 

crime_groups[is.na(crime_groups)] <- 0
## remove values with z-scores less than -2.8
for (i in 1:nrow(crime_groups)) {
  if (crime_groups$zscore[i] < (-2.5)) {
    crime_groups$n[i] <- crime_groups$mean[i]
   
  }
  
  else {
   TRUE == TRUE 
  }
}


```

```{r, warning=FALSE, include=FALSE}
library(reshape2)
library(devtools)
library(vars)

```


##Look for further gaps in data and get look at overall crime trends in Los Angeles


```{r, warning=FALSE}

##create subset of all crime by category 
crime_groups_melt <- crime_groups %>% group_by(Month_Year, Category) %>% tally()
##melt subset and set as DF
crime_groups_melt <- melt(crime_groups_melt, id=c("Month_Year", "Category", "nn"), na.rm=TRUE)
crime_groups_melt <- as.data.frame(crime_groups_melt)
##cast category to header 
crime_groups_melt <- dcast(crime_groups_melt, Month_Year ~ Category, value.var="nn")
crime_groups_melt <- as.data.frame(crime_groups_melt)

##create multivariate time series 
crime_groups_melt.ts <- ts(crime_groups_melt, frequency=12, start=c(2014))

```

```{r, message=FALSE, warning=FALSE}

library(ggfortify)

```

##Plot multivariate time series to see missing data and get look at general trends in city 
```{r, echo=FALSE}


autoplot(crime_groups_melt.ts)

```

```{r, warning=FALSE}

library(reshape2)
library(devtools)
library(vars)

```

#### Melt data to create average percent increase values for more precise look at trends 

```{r, warning=FALSE}

##create subset of all crime by category and area name 
crime_percent <- crime_groups %>% group_by(Month_Year, Area_Name, Category) %>% tally()
##melt subset and set as DF
crime_percent_melt <- melt(crime_percent, id=c("Month_Year", "Area_Name", "Category", "nn"), na.rm=TRUE)
crime_percent_melt <- as.data.frame(crime_percent_melt)
##cast category to header 
crime_percent_melt <- dcast(crime_percent_melt, Month_Year + Area_Name ~ Category, value.var="nn")
crime_percent_melt <- as.data.frame(crime_percent_melt)


##reset yearmon data-type and order vector by date 
crime_percent_melt$Month_Year <- as.yearmon(crime_percent_melt$Month_Year, "%b %Y")
crime_percent_melt <- crime_percent_melt[order(as.yearmon(crime_percent_melt$Month_Year, format="%b %Y")), ]

##use arrange function to also order by Area_Name for pct change calculation 
crime_percent_melt <- arrange(crime_percent_melt, Area_Name)

##instantiate new columns for percentage change

crime_percent_melt['Pct_Change_Ar'] <- 0
crime_percent_melt['Pct_Change_As'] <- 0
crime_percent_melt['Pct_Change_Ch'] <- 0
crime_percent_melt['Pct_Change_Ho'] <- 0
crime_percent_melt['Pct_Change_Ot'] <- 0
crime_percent_melt['Pct_Change_Ro'] <- 0
crime_percent_melt['Pct_Change_Se'] <- 0
crime_percent_melt['Pct_Change_Th'] <- 0

```


##loop through area name/category combos and calculate perentage change 

```{r, warning=FALSE}

for (i in 2:nrow(crime_percent_melt)) {
  if (crime_percent_melt$Area_Name[i] == crime_percent_melt$Area_Name[i-1]) {
crime_percent_melt$Pct_Change_Ar[i] <- ((crime_percent_melt$'Arson/Vandalism'[i] - crime_percent_melt$'Arson/Vandalism'[i-1]) /          crime_percent_melt$'Arson/Vandalism'[i-1]) * 100
  
crime_percent_melt$Pct_Change_As[i] <- ((crime_percent_melt$Assault[i] - crime_percent_melt$Assault[i-1]) / crime_percent_melt$Assault[i-1]) * 100

crime_percent_melt$Pct_Change_Ch[i] <- ((crime_percent_melt$Child_Abuse[i] - crime_percent_melt$Child_Abuse[i-1]) / crime_percent_melt$Child_Abuse[i-1]) * 100

crime_percent_melt$Pct_Change_Ho[i] <- ((crime_percent_melt$Homicide[i] - crime_percent_melt$Homicide[i-1]) / crime_percent_melt$Homicide[i-1]) * 100

crime_percent_melt$Pct_Change_Ot[i] <- ((crime_percent_melt$Other[i] - crime_percent_melt$Other[i-1]) / crime_percent_melt$Other[i-1]) * 100

crime_percent_melt$Pct_Change_Ro[i] <- ((crime_percent_melt$Robbery[i] - crime_percent_melt$Robbery[i-1]) / crime_percent_melt$Robbery[i-1]) * 100

crime_percent_melt$Pct_Change_Se[i] <- ((crime_percent_melt$Sexual[i] - crime_percent_melt$Sexual[i-1]) / crime_percent_melt$Sexual[i-1]) * 100

crime_percent_melt$Pct_Change_Th[i] <- ((crime_percent_melt$Theft[i] - crime_percent_melt$Theft[i-1]) / crime_percent_melt$Theft[i-1]) * 100
  }
}

```

## agregate and add percentage change to new df for analysis 

```{r, warning=FALSE} 

## remove unneccesary columns
crime_percent_change <- crime_percent_melt[c(1:2, 11:18)]
crime_percent_change[is.na(crime_percent_change)] <- 0

##create vector with just year
crime_percent_change['Year'] <- crime_percent_change$Month_Year
crime_percent_change$Year <- format(crime_percent_change$Year, "%Y")

##agregate data for average change per crime, per area

##create separate DF for just percentages, as agg function requires this 
crime_percents <- crime_percent_melt[c(11:18)]

##calculate total change in crime by year 
crime_change_year_total <- aggregate(crime_percent_change, list(Year = crime_percent_change$Year),  FUN=mean, na.rm=TRUE)

##calculate change in crime by year per area
crime_change_year_area <- aggregate(crime_percents, list(Year = crime_percent_change$Year, Area = crime_percent_change$Area_Name),  FUN=mean, na.rm=TRUE)

##write to CSV 
write.csv(crime_change_year_total, file="crime_change_year_total.csv")
write.csv(crime_change_year_area, file="crime_change_year_area.csv")

crime_percent_change['Date_Export'] <- as.Date(as.yearmon(crime_percent_change$Month_Year))
write.csv(crime_percent_change, file="crime_percent_change.csv")

```

##Create list with two features per neighborhood: Most common and fastest growing 

```{r, warning=FALSE}

## Change column names to standard format

crime_names <- as.character(unique(crime_groups$Category))
crime_names <- c("Year", "Area", crime_names)



## subset data for year 2016
crime_percent_change_2016 <- subset(crime_change_year_area, crime_change_year_area$Year == "2016")
names(crime_percent_change_2016) <- crime_names
##remove categories for which there are too few instances to justify targeted advertising 

crime_percent_change_2016$Child_Abuse <- NULL 
crime_percent_change_2016$Homicide <- NULL 
crime_percent_change_2016$Sexual <- NULL
crime_percent_change_2016$Other <- NULL

##create vector fastest growing crime and loop to find value 
crime_percent_change_2016['Fastest'] <- 0
for (i in 1:nrow(crime_percent_change_2016)) {
crime_percent_change_2016$Fastest[i] <- names(which.max( crime_percent_change_2016[i, (3:6) ]))
}

##create df for most-common crimes in 2016

crime_totals <- crime_groups
crime_totals$Month_Year <- as.yearmon(crime_totals$Month_Year, "%b %Y")
crime_totals['Year'] <- crime_totals$Month_Year
crime_totals$Year <- format(crime_totals$Month_Year, "%Y")
crime_totals <- crime_totals[, c(1:4, 10)]
crime_totals <- subset(crime_totals, crime_totals$Year == "2016")
head(crime_totals)
crime_totals <- crime_totals %>% group_by(Year, Area_Name, Category) %>% tally()

```

```{r, message=FALSE, warning=FALSE}
library(reshape2)
library(devtools)
library(vars)

```

##cast crime types to columns 

```{r, warning=FALSE}


crime_totals <- dcast(crime_totals, Year + Area_Name ~ Category, value.var="nn")
crime_totals <- as.data.frame(crime_totals)



crime_totals['Most_Common'] <- 0

for (i in 1:nrow(crime_totals)) {
crime_totals$Most_Common[i] <- names(which.max( crime_totals[i, (3:10) ]))
second_max <- max(crime_totals[i, (3:10) ][crime_totals[i, (3:10) ] != max(crime_totals [i, (3:10) ])])
crime_totals$Runner_Up[i] <- names(max(crime_totals[crime_totals[i, (3:10) ]!=max(crime_totals[i, (3:10) ])] ))
}

##standardize column mame
crime_percent_change_2016['Area_Name'] <- crime_percent_change_2016$Area
##merge two dfs into one for export 

crime_stats_2016 <- merge(crime_totals, crime_percent_change_2016, by="Area_Name")

##clean-up data by subsetting

crime_stats_2016 <- subset(crime_stats_2016, select=c("Area_Name", "Year.x", "Fastest", "Most_Common", "Arson/Vandalism.x", "Arson/Vandalism.y", "Assault.x", "Assault.y", "Child_Abuse", "Homicide", "Other", "Robbery.x", "Robbery.y", "Sexual", "Theft.x", "Theft.y"))

##clarify column names 

col_list <- c("Area_Name", "Year", "Fastest", "Most_Common", "Arson/Vandalism", "%Change_Arson/Vandalism", "Assault", "%Change_Assault", "Child_Abuse", "Homicide", "Other", "Robbery", "%Change_Robbery", "Sexual", "Theft", "%Change_Theft")

names(crime_stats_2016) <- col_list

write.csv(crime_stats_2016, "crime_stats.csv")

```

##create ts and decompose for target area/crime combos 


##Arson_77th

```{r, echo=FALSE}
##Arson_77th

Arson_77th <- subset(crime_groups, crime_groups$Area_Name == "77th Street" & crime_groups$Category == "Arson/Vandalism")

Arson_77th$Month_Year <- as.yearmon(Arson_77th$Month_Year, "%b %Y")
Arson_77th <- Arson_77th[order(as.yearmon(Arson_77th$Month_Year, format="%b %Y")), ]

Arson_77th.ts <- ts(Arson_77th$n, frequency=12, start=c(2014))

Arson_77th.ts.d <- decompose(Arson_77th.ts)


plot(Arson_77th.ts.d)

```

##Arson_Central

```{r, echo=FALSE}
##Arson_Central

Arson_Central <- subset(crime_groups, crime_groups$Area_Name == "Central" & crime_groups$Category == "Arson/Vandalism")

Arson_Central$Month_Year <- as.yearmon(Arson_Central$Month_Year, "%b %Y")
Arson_Central <- Arson_Central[order(as.yearmon(Arson_Central$Month_Year, format="%b %Y")), ]

Arson_Central.ts <- ts(Arson_Central$n, frequency=12, start=c(2014))

Arson_Central.ts.d <- decompose(Arson_Central.ts)


plot(Arson_Central.ts.d)

```





##Robbery_Devonshire

```{r, echo=FALSE}
##Robbery_Devonshire

Robbery_Devonshire <- subset(crime_groups, crime_groups$Area_Name == "Devonshire" & crime_groups$Category == "Robbery")

Robbery_Devonshire$Month_Year <- as.yearmon(Robbery_Devonshire$Month_Year, "%b %Y")
Robbery_Devonshire <- Robbery_Devonshire[order(as.yearmon(Robbery_Devonshire$Month_Year, format="%b %Y")), ]

Robbery_Devonshire.ts <- ts(Robbery_Devonshire$n, frequency=12, start=c(2014))

Robbery_Devonshire.ts.d <- decompose(Robbery_Devonshire.ts)


plot(Robbery_Devonshire.ts.d)

```








##Arson_Foothill

```{r, echo=FALSE}
##Arson_Foothill

Arson_Foothill <- subset(crime_groups, crime_groups$Area_Name == "Foothill" & crime_groups$Category == "Arson/Vandalism")

Arson_Foothill$Month_Year <- as.yearmon(Arson_Foothill$Month_Year, "%b %Y")
Arson_Foothill <- Arson_Foothill[order(as.yearmon(Arson_Foothill$Month_Year, format="%b %Y")), ]

Arson_Foothill.ts <- ts(Arson_Foothill$n, frequency=12, start=c(2014))

Arson_Foothill.ts.d <- decompose(Arson_Foothill.ts)


plot(Arson_Foothill.ts.d)

```




##Arson_Harbor

```{r, echo=FALSE}
##Arson_Harbor

Arson_Harbor <- subset(crime_groups, crime_groups$Area_Name == "Harbor" & crime_groups$Category == "Arson/Vandalism")

Arson_Harbor$Month_Year <- as.yearmon(Arson_Harbor$Month_Year, "%b %Y")
Arson_Harbor <- Arson_Harbor[order(as.yearmon(Arson_Harbor$Month_Year, format="%b %Y")), ]

Arson_Harbor.ts <- ts(Arson_Harbor$n, frequency=12, start=c(2014))

Arson_Harbor.ts.d <- decompose(Arson_Harbor.ts)


plot(Arson_Harbor.ts.d)

```



##Assault_Hollenbeck

```{r, echo=FALSE}
##Assault_Hollenbeck

Assault_Hollenbeck <- subset(crime_groups, crime_groups$Area_Name == "Hollenbeck" & crime_groups$Category == "Assault")

Assault_Hollenbeck$Month_Year <- as.yearmon(Assault_Hollenbeck$Month_Year, "%b %Y")
Assault_Hollenbeck <- Assault_Hollenbeck[order(as.yearmon(Assault_Hollenbeck$Month_Year, format="%b %Y")), ]

Assault_Hollenbeck.ts <- ts(Assault_Hollenbeck$n, frequency=12, start=c(2014))

Assault_Hollenbeck.ts.d <- decompose(Assault_Hollenbeck.ts)


plot(Assault_Hollenbeck.ts.d)

```


##Arson_Hollywood

```{r, echo=FALSE}
##Arson_Hollywood

Arson_Hollywood <- subset(crime_groups, crime_groups$Area_Name == "Hollywood" & crime_groups$Category == "Arson/Vandalism")

Arson_Hollywood$Month_Year <- as.yearmon(Arson_Hollywood$Month_Year, "%b %Y")
Arson_Hollywood <- Arson_Hollywood[order(as.yearmon(Arson_Hollywood$Month_Year, format="%b %Y")), ]

Arson_Hollywood.ts <- ts(Arson_Hollywood$n, frequency=12, start=c(2014))

Arson_Hollywood.ts.d <- decompose(Arson_Hollywood.ts)


plot(Arson_Hollywood.ts.d)

```




##Arson_Mission

```{r, echo=FALSE}
##Arson_Mission

Arson_Mission <- subset(crime_groups, crime_groups$Area_Name == "Mission" & crime_groups$Category == "Arson/Vandalism")

Arson_Mission$Month_Year <- as.yearmon(Arson_Mission$Month_Year, "%b %Y")
Arson_Mission <- Arson_Mission[order(as.yearmon(Arson_Mission$Month_Year, format="%b %Y")), ]

Arson_Mission.ts <- ts(Arson_Mission$n, frequency=12, start=c(2014))

Arson_Mission.ts.d <- decompose(Arson_Mission.ts)


plot(Arson_Mission.ts.d)

```

##Robbery_N_Hollywood

```{r, echo=FALSE}
##Robbery_N_Hollywood

Robbery_N_Hollywood <- subset(crime_groups, crime_groups$Area_Name == "N Hollywood" & crime_groups$Category == "Robbery")

Robbery_N_Hollywood$Month_Year <- as.yearmon(Robbery_N_Hollywood$Month_Year, "%b %Y")
Robbery_N_Hollywood <- Robbery_N_Hollywood[order(as.yearmon(Robbery_N_Hollywood$Month_Year, format="%b %Y")), ]

Robbery_N_Hollywood.ts <- ts(Robbery_N_Hollywood$n, frequency=12, start=c(2014))

Robbery_N_Hollywood.ts.d <- decompose(Robbery_N_Hollywood.ts)


plot(Robbery_N_Hollywood.ts.d)

```


##Arson_Newton

```{r, echo=FALSE}
##Arson_Newton

Arson_Newton <- subset(crime_groups, crime_groups$Area_Name == "Newton" & crime_groups$Category == "Arson/Vandalism")

Arson_Newton$Month_Year <- as.yearmon(Arson_Newton$Month_Year, "%b %Y")
Arson_Newton <- Arson_Newton[order(as.yearmon(Arson_Newton$Month_Year, format="%b %Y")), ]

Arson_Newton.ts <- ts(Arson_Newton$n, frequency=12, start=c(2014))

Arson_Newton.ts.d <- decompose(Arson_Newton.ts)


plot(Arson_Newton.ts.d)

```

##Arson_Northeast

```{r, echo=FALSE}
##Arson_Northeast

Arson_Northeast <- subset(crime_groups, crime_groups$Area_Name == "Northeast" & crime_groups$Category == "Assault")

Arson_Northeast$Month_Year <- as.yearmon(Arson_Northeast$Month_Year, "%b %Y")
Arson_Northeast <- Arson_Northeast[order(as.yearmon(Arson_Northeast$Month_Year, format="%b %Y")), ]

Arson_Northeast.ts <- ts(Arson_Northeast$n, frequency=12, start=c(2014))

Arson_Northeast.ts.d <- decompose(Arson_Northeast.ts)


plot(Arson_Northeast.ts.d)

```

##Arson_Olympic

```{r, echo=FALSE}
##Arson_Olympic

Arson_Olympic <- subset(crime_groups, crime_groups$Area_Name == "Olympic" & crime_groups$Category == "Arson/Vandalism")

Arson_Olympic$Month_Year <- as.yearmon(Arson_Olympic$Month_Year, "%b %Y")
Arson_Olympic <- Arson_Olympic[order(as.yearmon(Arson_Olympic$Month_Year, format="%b %Y")), ]

Arson_Olympic.ts <- ts(Arson_Olympic$n, frequency=12, start=c(2014))

Arson_Olympic.ts.d <- decompose(Arson_Olympic.ts)


plot(Arson_Olympic.ts.d)

```

##Assault_Pacific

```{r, echo=FALSE}
##Assault_Pacific

Assault_Pacific <- subset(crime_groups, crime_groups$Area_Name == "Pacific" & crime_groups$Category == "Assault")

Assault_Pacific$Month_Year <- as.yearmon(Assault_Pacific$Month_Year, "%b %Y")
Assault_Pacific <- Assault_Pacific[order(as.yearmon(Assault_Pacific$Month_Year, format="%b %Y")), ]

Assault_Pacific.ts <- ts(Assault_Pacific$n, frequency=12, start=c(2014))

Assault_Pacific.ts.d <- decompose(Assault_Pacific.ts)


plot(Assault_Pacific.ts.d)

```


##Arson_Rampart

```{r, echo=FALSE}
##Arson_Rampart

Arson_Rampart <- subset(crime_groups, crime_groups$Area_Name == "Rampart" & crime_groups$Category == "Arson/Vandalism")

Arson_Rampart$Month_Year <- as.yearmon(Arson_Rampart$Month_Year, "%b %Y")
Arson_Rampart <- Arson_Rampart[order(as.yearmon(Arson_Rampart$Month_Year, format="%b %Y")), ]

Arson_Rampart.ts <- ts(Arson_Rampart$n, frequency=12, start=c(2014))

Arson_Rampart.ts.d <- decompose(Arson_Rampart.ts)


plot(Arson_Rampart.ts.d)

```




##Arson_Southeast

```{r, echo=FALSE}
##Arson_Southeast

Arson_Southeast <- subset(crime_groups, crime_groups$Area_Name == "Southeast" & crime_groups$Category == "Arson/Vandalism")

Arson_Southeast$Month_Year <- as.yearmon(Arson_Southeast$Month_Year, "%b %Y")
Arson_Southeast <- Arson_Southeast[order(as.yearmon(Arson_Southeast$Month_Year, format="%b %Y")), ]

Arson_Southeast.ts <- ts(Arson_Southeast$n, frequency=12, start=c(2014))

Arson_Southeast.ts.d <- decompose(Arson_Southeast.ts)


plot(Arson_Southeast.ts.d)

```



##Arson_Southwest

```{r, echo=FALSE}
##Arson_Southwest

Arson_Southwest <- subset(crime_groups, crime_groups$Area_Name == "Southwest" & crime_groups$Category == "Arson/Vandalism")

Arson_Southwest$Month_Year <- as.yearmon(Arson_Southwest$Month_Year, "%b %Y")
Arson_Southwest <- Arson_Southwest[order(as.yearmon(Arson_Southwest$Month_Year, format="%b %Y")), ]

Arson_Southwest.ts <- ts(Arson_Southwest$n, frequency=12, start=c(2014))

Arson_Southwest.ts.d <- decompose(Arson_Southwest.ts)


plot(Arson_Southwest.ts.d)

```


##Arson_Topanga

```{r, echo=FALSE}
##Arson_Topanga

Arson_Topanga <- subset(crime_groups, crime_groups$Area_Name == "Topanga" & crime_groups$Category == "Arson/Vandalism")

Arson_Topanga$Month_Year <- as.yearmon(Arson_Topanga$Month_Year, "%b %Y")
Arson_Topanga <- Arson_Topanga[order(as.yearmon(Arson_Topanga$Month_Year, format="%b %Y")), ]

Arson_Topanga.ts <- ts(Arson_Topanga$n, frequency=12, start=c(2014))

Arson_Topanga.ts.d <- decompose(Arson_Topanga.ts)


plot(Arson_Topanga.ts.d)

```


##Arson_Van_Nuys

```{r, echo=FALSE}
##Arson_Van_Nuys

Arson_Van_Nuys <- subset(crime_groups, crime_groups$Area_Name == "Van Nuys" & crime_groups$Category == "Arson/Vandalism")

Arson_Van_Nuys$Month_Year <- as.yearmon(Arson_Van_Nuys$Month_Year, "%b %Y")
Arson_Van_Nuys <- Arson_Van_Nuys[order(as.yearmon(Arson_Van_Nuys$Month_Year, format="%b %Y")), ]

Arson_Van_Nuys.ts <- ts(Arson_Van_Nuys$n, frequency=12, start=c(2014))

Arson_Van_Nuys.ts.d <- decompose(Arson_Van_Nuys.ts)


plot(Arson_Van_Nuys.ts.d)

```


##Assault_West_LA

```{r, echo=FALSE}
##Assault_West_LA

Assault_West_LA <- subset(crime_groups, crime_groups$Area_Name == "West LA" & crime_groups$Category == "Assault")

Assault_West_LA$Month_Year <- as.yearmon(Assault_West_LA$Month_Year, "%b %Y")
Assault_West_LA <- Assault_West_LA[order(as.yearmon(Assault_West_LA$Month_Year, format="%b %Y")), ]

Assault_West_LA.ts <- ts(Assault_West_LA$n, frequency=12, start=c(2014))

Assault_West_LA.ts.d <- decompose(Assault_West_LA.ts)


plot(Assault_West_LA.ts.d)

```





##Arson_West_Valley

```{r, echo=FALSE}
##Arson_West_Valley

Arson_West_Valley <- subset(crime_groups, crime_groups$Area_Name == "West Valley" & crime_groups$Category == "Arson/Vandalism")

Arson_West_Valley$Month_Year <- as.yearmon(Arson_West_Valley$Month_Year, "%b %Y")
Arson_West_Valley <- Arson_West_Valley[order(as.yearmon(Arson_West_Valley$Month_Year, format="%b %Y")), ]

Arson_West_Valley.ts <- ts(Arson_West_Valley$n, frequency=12, start=c(2014))

Arson_West_Valley.ts.d <- decompose(Arson_West_Valley.ts)


plot(Arson_West_Valley.ts.d)

```

##Arson_Wilshire

```{r, echo=FALSE}
##Arson_Wilshire

Arson_Wilshire <- subset(crime_groups, crime_groups$Area_Name == "Wilshire" & crime_groups$Category == "Arson/Vandalism")

Arson_Wilshire$Month_Year <- as.yearmon(Arson_Wilshire$Month_Year, "%b %Y")
Arson_Wilshire <- Arson_Wilshire[order(as.yearmon(Arson_Wilshire$Month_Year, format="%b %Y")), ]

Arson_Wilshire.ts <- ts(Arson_Wilshire$n, frequency=12, start=c(2014))

Arson_Wilshire.ts.d <- decompose(Arson_Wilshire.ts)


plot(Arson_Wilshire.ts.d)

```

## forecast crime 

```{r}
require(tseries)
adf.test(diff(diff(log(Arson_Newton.ts))))
adf.test(diff(diff(log(Assault_Hollenbeck.ts))))
adf.test(diff(diff(log(Arson_77th.ts))))
```

#create standard ARIMA model with no differencing to see what changes are neccesary

```{r}
library(forecast)  
library(stats)
 
fit_1<- arima(Arson_Newton.ts, c(0,0,0))
fit_2<- arima(Assault_Hollenbeck.ts, c(0,0,0))
fit_3 <- arima(Arson_77th.ts, c(0,0,0))

```

```{r, echo=FALSE, warning=FALSE}

tsdiag(fit_1)
```

```{r}


fit_Arson_Newton<- auto.arima(Arson_Newton.ts)
fit_Arson_Newton
fit_Arson_Newton <- arima(Arson_Newton.ts, c(0, 1, 0))

fit_Arson_77th <- auto.arima(Arson_77th.ts)
fit_Arson_77th

fit_Arson_77th <- arima(Arson_77th.ts, c(0, 0, 0))

fit_Assault_Hollenbeck <- auto.arima(Assault_Hollenbeck.ts)
fit_Assault_Hollenbeck

fit_Arson_77th <- arima(Arson_77th.ts, c(1, 1, 0))



```

#HoltWinters for Arson/77th
```{r, echo = FALSE}

Arson_77th.Holt <- HoltWinters(Arson_77th.ts, gamma=TRUE)
plot(Arson_77th.Holt)

Arson_77th.forecast <- forecast.HoltWinters(Arson_77th.Holt, h=12)
plot(Arson_77th.forecast)

```

#HoltWinters for Assault/Hollenbeck 
```{r, echo = FALSE}

Assault_Hollenbeck.Holt <- HoltWinters(Assault_Hollenbeck.ts, gamma=TRUE)
plot(Assault_Hollenbeck.Holt)

Assault_Hollenbeck.forecast <- forecast.HoltWinters(Assault_Hollenbeck.Holt, h=12)
plot(Assault_Hollenbeck.forecast)

```

#HoltWinters for Arson/Newton 
```{r, echo = FALSE}

Arson_Newton.Holt <- HoltWinters(Arson_Newton.ts, gamma=TRUE)
plot(Arson_Newton.Holt)

Arson_Newton.forecast <- forecast.HoltWinters(Arson_Newton.Holt, h=12)
plot(Arson_Newton.forecast)

```



# Plot Arson_Newton with ARIMA 
```{r, echo=FALSE}
tsdiag(fit_Arson_Newton)

forecast.Arson_Newton <- forecast.Arima(fit_Arson_Newton, h=12)
plot(forecast.Arson_Newton)
```

# Plot Arson_77th 
```{r, echo=FALSE}
tsdiag(fit_Arson_Newton)

forecast.Arson_77th <- forecast.Arima(fit_Arson_77th, h=12)
plot(forecast.Arson_77th)
```


# Plot Arson_77th 
```{r, echo=FALSE}
tsdiag(fit_Arson_Newton)

forecast.Assault_Hollenbeck <- forecast.Arima(fit_Assault_Hollenbeck, h=12)
plot(forecast.Assault_Hollenbeck )
```
